Chlorophylla

### 2019-02-28 Chlorophyll_a .Rmd
updated

# Pixels and matching
match_index <- knnx.index(data = as.matrix(daily_chloro_data[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

# # # Select SST pixels nearest to insitu sites
pixel_match <- daily_chloro_data[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

@@

>>>>

unique_pixel <- MODIS_Chloro %>%
  select(lon, lat) %>%
  unique()

# # Select nearest 1 pixels (k = 1)
# # here we use knnx to find the closes 1 pixels to the insitu sites
match_index <- knnx.index(data = as.matrix(MODIS_Chloro[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

# # # Select SST pixels nearest to insitu sites
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

@@

```{r}
daily_chloro_data <- MODIS_Chloro %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  mutate(month = month(date),
         day = day(date),
         year = year(date)) %>% 
  dplyr::group_by(lon, lat, day, month, year) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE))

match_index <- knnx.index(data = as.matrix(daily_chloro_data[,1:2]),
                          query = as.matrix(combined_US[,5:6]), k = 1)

pixel_match <- daily_chloro_data[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = combined_US$site)

# With the chloro pixels filter, it is now faster to create the daily data
daily_chloro_data <- daily_chloro_match %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>% 
  dplyr::group_by(combi, lon, lat) %>% 
  tidyr::nest() %>% 
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                       climatologyPeriod = c("2002-07-13", "2018-12-04"), # This doesn't mean anything, but the function needs it to work
                       maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>% 
  tidyr::unnest() %>% 
  select(-doy, -seas, -thresh)
```
